Validating FF-Replan vs.\@ a State-Of-The-Art Probabilistic Planner in Translated Real World Domains

### 2014-03-30 FinalPaper/paper.tex
Improve first sentence of the introduction, remove incorporate.

Since the first incorporation of the International Probabilistic Planning
Competition (IPPC), it has undergone radical changes. Dominating planners
of previous incorporations had a strong focus on goal-oriented MDPs,
determinizing and using powerful classical planners (e.g. FF
\cite{Hoffmann01theff}) and replanning. New benchmarks have demonstrated
weaknesses in existing solution techniques.

>>>>

Since the first the International Probabilistic Planning Competition (IPPC),
problems have undergone radical changes. Dominating planners of previous
incorporations had a strong focus on goal-oriented MDPs, determinizing and
using powerful classical planners (e.g. FF \cite{Hoffmann01theff}) and
replanning. New benchmark problems have demonstrated weaknesses in existing
solution techniques.
